Fixes to the original paper

### 2015-10-01 introProtocol.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\section{Carrier Sense Multiple Access with Enhanced Collision Avoidance (CSMA/ECA)}

CSMA/ECA~\cite{barcelo2008lba} is a totally distributed and collision-free MAC for WLANs. It differs from CSMA/CA in that it uses a deterministic backoff, $B_{d}=CW_{\min}/2$ after successful transmissions, where $CW_{\min}$ is the minimum contention window of typical value $CW_{\min}=16$. By doing so, contenders that successfully transmitted on schedule $n$, will transmit without colliding with other successful nodes in future cycles.

@@

	\begin{algorithm}[tb]
	\While{the device is on}
	{
	  $r \leftarrow 0$ ; $k \leftarrow 0$\;
	  $b \leftarrow \mathcal{U}[0,2^k\rm{CW}_{min}-1]$\;
	  \While{there is a packet to transmit}{
	    %\tcc{Initialize $a$.}
	    \Repeat{($r = R$) or (success)}{
	      %\tcc{First, backoff.}
	      \While{$B>0$}{
	        wait 1 slot\;
	        $B \leftarrow B-1$\;
	      }
	      \colorbox{yellow}{Attempt transmission of $2^k$ packets;}\\
	      \If{collision}{
	        %\tcc{Random backoff.}
	        $r \leftarrow r+1$\;
	        $k \leftarrow \min (k+1,m)$\;
	        $B \leftarrow \mathcal{U}[0, 2^k  \rm{CW}_{min} -1]$\;
	      }
	    }
	    $r \leftarrow 0$\;
	    %$s \leftarrow 0$\;
	    \eIf{success}{
	      %\tcc{Random backoff.}
	      \colorbox{yellow}{$B_{d} \leftarrow (2^{k}\rm{CW}_{min})/2-1$;}\\
		$B \leftarrow B_{d}$;\\
	    }
	    {
	      Discard packet\;
	      $B \leftarrow \mathcal{U}[0, 2^k \rm{CW}_{min}-1]$\;
	    }
	  }
	  Wait until there is a packet to transmit\;
	}
	\vspace{0.2cm}
	\caption{CSMA/ECA$_{\text{Hys+FS}}$}
	\label{alg:fullECA}
	\end{algorithm}

@@

	\subsection{The effects of Aggregation}\label{effects-of-aggregation}
	Fair Share is an aggregation mechanism that coupled with the collision-free schedule built by CSMA/ECA$_{\text{Hys}}$ is able to provide short-term fairness. However, it also improves the throughput since the aggregation process makes the packet transmission more efficient by reducing overheads. The downside of Fair Share is that it may increase the time between two consecutive transmissions from the same node, which may affect negatively delay-sensitive applications such as gaming or high definition real-time video.

@@

	Since we consider that fairness and a short inter-transmission time are even more important than raw throughput for the next generation of WLANs, we keep CSMA/ECA$_{\text{Hys+FS}}$ as the reference protocol.

@@

	They correspond to the maximum and minimum achievable throughput without the possibility of collisions using Hysteresis and Fair Share. The ideal CSMA/ECA$_{\text{Hys+FS}}$ network uses the minimum schedule length that guarantees a collision-free operation. That is, with a schedule length of $C=2^{k}B_{d}$, where $k = \left\lceil log_{2}(N/B_{d})\right\rceil$). Using this minimum schedule length, $N$ nodes will be at the same backoff stage if $N\leq B_{d}$. Otherwise, $h = N-(C-N)$ nodes would occupy the $k$-th backoff stage and $N-h$ the immediate inferior backoff stage, i.e., the $(k-1)$-th one. The system throughput is computed as follows:

@@

>>>>

\section{Carrier Sense Multiple Access with Enhanced Collision Avoidance (CSMA/ECA)}\label{introProtocol}

CSMA/ECA~\cite{barcelo2008lba} is a fully distributed and collision-free MAC for WLANs. It differs from CSMA/CA in that it uses a deterministic backoff, $B_{d}=CW_{\min}/2$ after successful transmissions, where $CW_{\min}$ is the minimum contention window of typical value $CW_{\min}=16$. By doing so, contenders that successfully transmitted on schedule $n$, will transmit without colliding with other successful nodes in future cycles.

@@

	\begin{algorithm}[tb]
	\While{the device is on}
	{
	  $r \leftarrow 0$ ; $k \leftarrow 0$\;
	  $b \leftarrow \mathcal{U}[0,2^k\rm{CW}_{min}-1]$\;
	  \While{there is a packet to transmit}{
	    %\tcc{Initialize $a$.}
	    \Repeat{($r = R$) or (success)}{
	      %\tcc{First, backoff.}
	      \While{$B>0$}{
	        wait 1 slot\;
	        $B \leftarrow B-1$\;
	      }
	      \colorbox{yellow}{Attempt transmission of $2^k$ packets;}\\
	      \If{collision}{
	        %\tcc{Random backoff.}
	        $r \leftarrow r+1$\;
	        $k \leftarrow \min (k+1,m)$\;
	        $B \leftarrow \mathcal{U}[0, 2^k  \rm{CW}_{min} -1]$\;
	      }
	    }
	    $r \leftarrow 0$\;
	    %$s \leftarrow 0$\;
	    \eIf{success}{
	      %\tcc{Random backoff.}
	      \colorbox{yellow}{$B_{d} \leftarrow (2^{k}\rm{CW}_{min})/2-1$;}\\
		$B \leftarrow B_{d}$;\\
	    }
	    {
	      Discard packet\;
	      $k \leftarrow 0$\;
	      $B \leftarrow \mathcal{U}[0, 2^k \rm{CW}_{min}-1]$\;
	    }
	  }
	  Wait until there is a packet to transmit\;
	}
	\vspace{0.2cm}
	\caption{CSMA/ECA$_{\text{Hys+FS}}$}
	\label{alg:fullECA}
	\end{algorithm}

@@

	\textcolor{red}{We should also incorporate CSMA/CA$_{\text{FS}}$??.}

	\subsection{The effects of Aggregation}\label{effects-of-aggregation}
	Fair Share is an \textcolor{red}{A-MPDU} aggregation mechanism that coupled with the collision-free schedule built by CSMA/ECA$_{\text{Hys}}$ is able to provide short-term fairness. However, it also improves the throughput since the aggregation process makes the packet transmission more efficient by reducing overheads. The downside of Fair Share is that it may increase the time between two consecutive transmissions from the same node, which may affect negatively delay-sensitive applications such as gaming or high definition real-time video. \textcolor{red}{An example of the duration of a transmission is provided by (\ref{eq:Ts}) in the following Section~\ref{ECA-bounds}.}

@@

	Since we consider that fairness and a short inter-transmission time are even more important than raw throughput for the next generation of WLANs, we keep CSMA/ECA$_{\text{Hys+FS}}$ as the reference protocol. \textcolor{red}{Is this still true?}

@@

	They correspond to the maximum and minimum achievable throughput without the possibility of collisions using Hysteresis and Fair Share. The ideal CSMA/ECA$_{\text{Hys+FS}}$ network uses the minimum schedule length that guarantees a collision-free operation. That is, with a schedule length of $C=2^{k}B_{d}$, where $k = \left\lceil log_{2}(N/B_{d})\right\rceil$. Using this minimum schedule length, $N$ nodes will be at the same backoff stage if $N\leq B_{d}$. Otherwise, $h = N-(C-N)$ nodes would occupy the $k$-th backoff stage and the other $N-h$ \textcolor{red}{nodes the $(k-1)$-th one}. The system throughput is computed as follows:

@@

	\textcolor{red}{\subsection{Real hardware implementation} 
	Replacing the firmware of commercial WLAN cards with the Open Firmware for WiFi Networks, OpenFWWF~\cite{OpenFWWF}, allows the modification of time-sensitive operations in the MAC, like the backoff procedure. In Section~\ref{EDCA} we provide details regarding the tesbed, the firmware used and present results of real experiments using CSMA/ECA.}

### 2015-10-01 journal.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\blfootnote{This work was partially supported by the Spanish government, through the project CISNETS (TEC2012-32354).\\
L. Sanabria-Russo (\href{mailto:luis.sanabria@upf.edu}{luis.sanabria@upf.edu}) , J. Barcelo (\href{mailto:jaume.barcelo@upf.edu}{jaume.barcelo@upf.edu}) and B. Bellalta (\href{mailto:boris.bellalta@upf.edu}{boris.bellalta@upf.edu}) are with the Department of Information and Communication Technologies, Universitat Pompeu Fabra, Barcelona, Spain.}
%(e-mails: \href{mailto:luis.sanabria@upf.edu}{luis.sanabria@upf.edu}, \href{mailto:jaume.barcelo@upf.edu}{jaume.barcelo@upf.edu}, \href{mailto:boris.bellalta@upf.edu}{boris.bellalta@upf.edu})

@@

\boldmath Collisions are a main cause of throughput degradation in WLANs. The current contention mechanism used in IEEE 802.11 networks is called Carrier Sense Multiple Access with Collision Avoidance (CSMA/CA). It uses a Binary Exponential Backoff (BEB) technique to randomise each contender attempt of transmitting, effectively reducing the collision probability. Nevertheless, CSMA/CA relies on a random backoff that while effective and totally distributed, in principle is unable to completely eliminate collisions, therefore degrading the network throughput as more contenders attempt to share the channel. Carrier Sense Multiple Access with Enhanced Collision Avoidance (CSMA/ECA) is able to create a collision-free schedule in a totally distributed manner using a deterministic backoff after successful transmissions. Hysteresis and Fair Share are two extensions of CSMA/ECA to support a large number of contenders in a collision-free schedule. CSMA/ECA offers better throughput than CSMA/CA and short-term throughput fairness.

@@

This paper fills those gaps by extending~\cite{research2standards}, and consolidates the push of CSMA/ECA as a potential replacement of CSMA/CA for next generation WLANs. In detail, this paper provides the following contributions:

\begin{itemize}
	\item First results on the achievable throughput and delay of CSMA/ECA with Hysteresis and Fair Share under non-saturated traffic conditions for very large number of nodes.
	\item The impact of imperfect clocks on CSMA/ECA with Hysteresis and Fair Share's deterministic backoff and its consequences on the achieved performance.
	\item Formulation of the throughput bounds for CSMA/ECA with Hysteresis and Fair Share.
	\item Coexistence and backwards compatibility with CSMA/CA nodes under different traffic conditions.
%	\item Overview of real hardware implementations of CSMA/ECA prototypes.
\end{itemize}

Results show that CSMA/ECA with Hysteresis and Fair Share is capable of accommodating many users in collision-free schedules. Further, the coexistence tests show that the average aggregated throughput of a mixed network is higher than the observed in CSMA/CA-only networks, as well as a high resilience to clock-drifts.

Beyond simulations results, the implementation of CSMA/ECA prototypes\cite{ECA-DEMO-INFOCOM14, sanabria2013prototyping, BECA-test} show that the construction of collision-free schedules using a deterministic backoff after successful transmissions is possible and results in a throughput increase by reducing the number of corrupted frames.

@@

\input{relatedWork}\label{relatedWork}
\input{introProtocol}\label{introProtocol}
\input{simulations}\label{simulations}		
\input{results}\label{results}
\input{realImplementation}\label{EDCA}
\input{transition}\label{ECAtoCA}

>>>>

\blfootnote{This work was partially supported by the Spanish government, through the project CISNETS (TEC2012-32354).\\
L. Sanabria-Russo (\href{mailto:luis.sanabria@upf.edu}{luis.sanabria@upf.edu}) , J. Barcelo (\href{mfullyailto:jaume.barcelo@upf.edu}{jaume.barcelo@upf.edu}) and B. Bellalta (\href{mailto:boris.bellalta@upf.edu}{boris.bellalta@upf.edu}) are with the Department of Information and Communication Technologies, Universitat Pompeu Fabra, Barcelona, Spain.}
%(e-mails: \href{mailto:luis.sanabria@upf.edu}{luis.sanabria@upf.edu}, \href{mailto:jaume.barcelo@upf.edu}{jaume.barcelo@upf.edu}, \href{mailto:boris.bellalta@upf.edu}{boris.bellalta@upf.edu})

@@

\boldmath Collisions are a main cause of throughput degradation in WLANs. The current contention mechanism used in IEEE 802.11 networks is called Carrier Sense Multiple Access with Collision Avoidance (CSMA/CA). It uses a Binary Exponential Backoff (BEB) technique to randomise each contender attempt of transmitting, effectively reducing the collision probability. Nevertheless, CSMA/CA relies on a random backoff that while effective and fully distributed, in principle is unable to completely eliminate collisions, therefore degrading the network throughput as more contenders attempt to share the channel. Carrier Sense Multiple Access with Enhanced Collision Avoidance (CSMA/ECA) is able to create a collision-free schedule in a fully distributed manner using a deterministic backoff after successful transmissions. Hysteresis and Fair Share are two extensions of CSMA/ECA to support a large number of contenders in a collision-free schedule. CSMA/ECA offers better throughput than CSMA/CA and short-term throughput fairness.

@@

\textcolor{red}{In this part we should also assess the channel error scenario and the real implementation with OpenFWWF.}

This paper fills those gaps by extending~\cite{research2standards}, and consolidates the push for CSMA/ECA as a potential replacement of CSMA/CA for next generation WLANs. In detail, this paper provides the following contributions:

\begin{itemize}
	\item First results on the achievable throughput and delay of CSMA/ECA with Hysteresis and Fair Share under non-saturated traffic conditions for very large number of nodes.
	\item The impact of imperfect clocks on CSMA/ECA with Hysteresis and Fair Share's deterministic backoff and its consequences on the achieved performance.
	\textcolor{red}{\item The effect of channel errors over collision-free schedules and how to solve the issue of converging rapidly to the biggest cycle length with the Schedule Reset mechanism.}
	\item Formulation of the throughput bounds for CSMA/ECA with Hysteresis and Fair Share.
	\item Coexistence and backwards compatibility with CSMA/CA nodes under different traffic conditions.
	\item Implementation of CSMA/ECA in real hardware.
\end{itemize}

%Results show that CSMA/ECA with Hysteresis and Fair Share is capable of accommodating many users in collision-free schedules. Further, the coexistence tests show that the average aggregated throughput of a mixed network is higher than that observed in CSMA/CA-only networks, as well as a high resilience to clock-drifts.
\textcolor{red}{Results, derived from a modified version of the COST~\cite{COST} simulator, show that CSMA/ECA with Hysteresis and Fair Share is capable of accommodating many users in collision-free schedules. Further, as tests in a mixed network with different proportions of CSMA/CA and CSMA/ECA nodes show, the aggregated throughput is higher than the observed in CSMA/CA-only networks without significant sacrifice from legacy stations.}

Beyond simulations results, the implementation of CSMA/ECA prototypes\cite{ECA-DEMO-INFOCOM14, sanabria2013prototyping, BECA-test,CF-MAC} show that the construction of collision-free schedules using a deterministic backoff after successful transmissions is possible and results in a throughput increase by reducing the number of corrupted frames.\textcolor{red}{We then present the first real hardware implementation of CSMA/ECA with Hysteresis. Results show that indeed it is able of providing higher throughput and lower collisions than CSMA/CA for the same number of contenders.}

@@

\input{relatedWork}
\input{introProtocol}
\input{simulations}
\input{results}
\input{realImplementation}
\input{transition}

### 2015-10-01 realImplementation.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\section{Real hardware implementation}
The implementation of CSMA/ECA$_{\text{Hys+FS}}$ should be carried out at a firmware level due to the tight timing constrains related to the backoff procedure. There are several alternatives to modify the backoff operation in WNICs, either using open firmware like OpenFWWF~\cite{OpenFWWF} or through Field Programmable Gate Arrays (FPGA).

>>>>

\section{Real hardware implementation}\label{EDCA}
The implementation of CSMA/ECA$_{\text{Hys+FS}}$ should be carried out at a firmware level due to the tight timing constrains related to the backoff procedure. There are several alternatives to modify the backoff operation in WNICs, either using open firmware like OpenFWWF~\cite{OpenFWWF} or through Field Programmable Gate Arrays (FPGA).

### 2015-10-01 relatedWork.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\section{Related Work}
Time in WLANs is divided into tiny empty slots of fixed length $\sigma_{e}$, collisions and successful slots of length $\sigma_{c}$ and $\sigma_{s}$, respectively. Collision and successful slots contain collisions or successful transmissions, making them several orders of magnitude larger than empty slots ($\sigma_{e}\ll\min(\sigma_{s},\sigma_{c}))$. One of the effects of collisions is the degradation of the network performance by wasting channel time on collisions slots.

Recent advances in the WLANs PHY~\cite{perahia2008ieee,6191306} push the research community towards the development of MAC protocols able to take advantage of a much faster PHY. By reducing the time spent in collisions nodes are able to transmit more often, which in turn translates to an increase in the network throughput. Further, the upcoming MAC protocols for WLANs should work without message exchange between contenders, that is, work in a totally distributed fashion in order to avoid injecting extra control traffic that may reduce the data throughput.

The followings are MAC protocols for WLANs, distributed and capable of attaining greater throughput than CSMA/CA by constructing a collision-free schedule.

@@

Zero Collision MAC (ZC-MAC)~\cite{ZMAC} achieves a zero collision schedule for WLANs in a totally distributed way. It does so by allowing contenders to reserve one empty slot from a predefined virtual schedule of $N$-slots in length. Backlogged stations pick a slot in the virtual cycle to attempt transmission. If two or more stations picked the same slot in the cycle, their transmissions will eventually collide. This forces the involved contenders to randomly and uniformly select other empty slot from those detected empty in the previous cycle plus the slot where they collided. When all $M$ stations reserve a different slot, a collision-free schedule is achieved.

ZC-MAC is able to outperform CSMA/CA under different scenarios. Nevertheless, given that the length of ZC MAC's virtual cycle has to be predefined without actual knowledge of the real number of contenders in the deployment, the protocol is unable to provide a collision-free schedule when $M>N$. Furthermore, if $N$ is overestimated ($N\gg M$), the fixed-width empty slots between each contender's successful transmission are no longer negligible and contribute to the degradation of the network performance. Additionally, Z-MAC nodes require common knowledge of where the virtual schedule starts/ends. This is not considered in CSMA/CA and constitutes an obstacle towards standardisation.

@@

>>>>

\section{Related Work}\label{relatedWork}
Time in WLANs is divided into tiny empty slots of fixed length $\sigma_{e}$, collisions, and successful slots of length $\sigma_{c}$ and $\sigma_{s}$, respectively. Collision and successful slots contain collisions or successful transmissions, making them several orders of magnitude larger than empty slots ($\sigma_{e}\ll\min(\sigma_{s},\sigma_{c}))$. One of the effects of collisions is the degradation of the network performance by wasting channel time on collisions slots.

Recent advances in the WLANs PHY~\cite{perahia2008ieee,6191306} push the research community towards the development of MAC protocols able to take advantage of a much faster PHY. By reducing the time spent in collisions nodes are able to transmit more often, which in turn translates to an increase in the network throughput. Further, the upcoming MAC protocols for WLANs should work without message exchange between contenders, that is, work in a fully distributed fashion in order to avoid injecting extra control traffic that may reduce the data throughput.

The following are MAC protocols for WLANs, distributed and capable of attaining greater throughput than CSMA/CA by constructing a collision-free schedule.

@@

Zero Collision MAC (ZC-MAC)~\cite{ZMAC} achieves a zero collision schedule for WLANs in a fully distributed way. It does so by allowing contenders to reserve one empty slot from a predefined virtual schedule of $N$-slots in length. Backlogged stations pick a slot in the virtual cycle to attempt transmission. If two or more stations picked the same slot in the cycle, their transmissions will eventually collide. This forces the involved contenders to randomly and uniformly select other empty slot from those detected empty in the previous cycle plus the slot where they collided. When all $M$ stations reserve a different slot, a collision-free schedule is achieved.

ZC-MAC is able to outperform CSMA/CA under different scenarios. Nevertheless, given that the length of ZC MAC's virtual cycle has to be predefined without actual knowledge of the real number of contenders in the deployment, the protocol is unable to provide a collision-free schedule when $M>N$. Furthermore, if $N$ is overestimated ($N\gg M$), the fixed-width empty slots between each contender's successful transmission are no longer negligible and contribute to the degradation of the network performance\textcolor{red}{\footnote{\textcolor{red}{With a very large $N$ and $M\leq N$, the overall aggregated throughput will start to decrease as $M\rightarrow N$. This is due to the very big period of time between successful transmissions. For the opposite case, that is $M>N$, the same effect is produced albeit with an increased number of collisions.}}}. Additionally, Z-MAC nodes require common knowledge of where the virtual schedule starts/ends. This is not considered in CSMA/CA and constitutes an obstacle towards standardisation.

@@

\textcolor{red}{NOTE: We should show the performance of L-ZC and L-MAC alongisde Basic CSMA/ECA. It is very important to define L-ZC given that the paper only talks about ZC. Also, we should clarify that the virtual schedule size is the same for all contenders, but they are not need to have an universal view of it.}

### 2015-10-01 results.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\section{Results}

@@

	\subsection{Non-saturated nodes}\label{resultsUnsaturated}
	Emptying the MAC queue in CSMA/ECA$_{\text{Hys+FS}}$ means that nodes will reset their backoff stage and use a random backoff when a new packet arrives at the queue, breaking the collision-free schedule (if any) for CSMA/ECA$_{\text{Hys+FS}}$ contenders. The followings show the impact over throughput, delay and time between successful transmissions when using CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ in non-saturated conditions.\\

>>>>

\section{Results}\label{results}

@@

	\subsection{Non-saturated nodes}\label{resultsUnsaturated}
	Emptying the MAC queue in CSMA/ECA$_{\text{Hys+FS}}$ means that nodes will reset their backoff stage and use a random backoff when a new packet arrives at the queue, breaking the collision-free schedule (if any) for CSMA/ECA$_{\text{Hys+FS}}$ contenders. The following show the impact over throughput, delay and time between successful transmissions when using CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ in non-saturated conditions.\\

### 2015-10-01 simulations.tex
Finished with the first reviewer. There still work to be done regarding the figures to complete his suggestions

\section{Simulation Scenario}
This section provides the simulation parameters for testing CSMA/ECA$_{\text{Hys+FS}}$ under two different traffic conditions, namely saturated and non-saturated. Further, the simulation of the clock drift effect, and the coexistence with CSMA/CA are also subjects to be addressed in this section.

@@

	\begin{itemize}
		\item Unspecified parameters follow the IEEE 802.11n ($2.4$~GHz) standard.
		\item All nodes are in communication range.
		\item No Request-to-Send (RTS) or Clear-to-Send (CTS) messages are used.
		\item There are no external interference or channel errors.
		\item Collisions take as much channel time as successful transmissions.
	\end{itemize}

	The aforementioned assumptions ensure that the simulation results are just effects of the MAC behavior, thus isolating it from external factors, i.e.: channel imperfections. Further, in a collision-free CSMA/ECA$_{\text{Hys+FS}}$ operation there is no need for RTS/CTS mechanisms, given that successful nodes already know their respective transmission slot.

	If not mentioned otherwise, results are derived from 100 simulations of 100 seconds in length. Figures show $95$\% confidence intervals.

	\begin{table}
		\centering
		\caption{PHY and MAC parameters for the simulations}
		\label{tab:mac-params}
		\begin{tabular}{|c|c|}
			\hline
			\multicolumn{2}{|c|}{{\bfseries PHY}}\\
			\hline
			{\bfseries Parameter} & {\bfseries Value}\\
			\hline
			PHY rate & 65~Mbps\\
			Empty slot & $9~\mu s$\\
			DIFS & $28~\mu s$\\
			SIFS & $10~\mu s$\\
			\hline
			\multicolumn{2}{|c|}{{\bfseries MAC}}\\
			\hline
			{\bfseries Parameter} & {\bfseries Value}\\
			\hline
			Maximum backoff stage ($m$) & 5\\
			Minium Contention Window ($CW_{\min}$) & 16\\
			Maximum retransmission attempts & 6\\
			Packet size (Bytes) & 1024\\
			MAC queue size (Packets) & 1000\\
			\hline
		\end{tabular}
	\end{table}

@@

>>>>

\section{Simulation Scenario}\label{simulations}
This section provides the simulation parameters for testing CSMA/ECA$_{\text{Hys+FS}}$ under two different traffic conditions, namely saturated and non-saturated. Further, the simulation of the clock drift effect, and the coexistence with CSMA/CA are also subjects to be addressed in this section.

@@

	\begin{itemize}
		\item Unspecified parameters follow the IEEE 802.11n ($2.4$~GHz) standard.
		\item All nodes are in communication range.
		\item No Request-to-Send (RTS) or Clear-to-Send (CTS) messages are used.
		\item There are no external interference or channel errors. \textcolor{red}{Remove}.
		\item Collisions take as much channel time as successful transmissions.
	\end{itemize}

	The aforementioned assumptions ensure that the simulation results are just effects of the MAC behavior, thus isolating it from external factors, i.e.: \textcolor{red}{channel imperfections}. Further, in a collision-free CSMA/ECA$_{\text{Hys+FS}}$ operation there is no need for RTS/CTS mechanisms, given that successful nodes already know their respective transmission slot. \textcolor{red}{Maybe here is where the conversation about hidden nodes should take place?}

	If not mentioned otherwise, results are derived from 100 simulations of 100 seconds in length. Figures also show the standard deviation.

	\begin{table}
		\centering
		\caption{PHY and MAC parameters for the simulations \textcolor{red}{REVIEW}}
		\label{tab:mac-params}
		\begin{tabular}{|c|c|}
			\hline
			\multicolumn{2}{|c|}{{\bfseries PHY}}\\
			\hline
			{\bfseries Parameter} & {\bfseries Value}\\
			\hline
			PHY rate & 65~Mbps\\
			Empty slot & $9~\mu s$\\
			DIFS & $28~\mu s$\\
			SIFS & $10~\mu s$\\
			\hline
			\multicolumn{2}{|c|}{{\bfseries MAC}}\\
			\hline
			{\bfseries Parameter} & {\bfseries Value}\\
			\hline
			Maximum backoff stage ($m$) & 5\\
			Minium Contention Window ($CW_{\min}$) & 16\\
			Maximum retransmission attempts & 6\\
			Packet size (Bytes) & 1024\\
			MAC queue size (Packets) & 1000\\
			\hline
		\end{tabular}
	\end{table}

@@

	\textcolor{red}{\subsection{Channel errors} Here we explain how we implement our channel errors model}.
